PyKE: Open source Python data analysis for NASA's Kepler, K2, and TESS missions

### 2018-01-17 paper/ms.tex
unfortunately, tectonic does not support ps images :(
vuala travis

A runnable example of SAP flux correction for target \texttt{KOI 008462852}
can be written as follows
\begin{verbatim}
from pyke.lightcurve import KeplerCBVCorrector
cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
                         "0084/008462852/kplr008462852-2011073133259_llc.fits")
cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

As a result, Fig~\ref{fig:cbv-correction} illustrates the correction.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv.eps}
    \caption{CBV correction applied on \texttt{KOI 008462852}}
    \label{fig:cbv-correction}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-grid-search.eps}
    \caption{Grid search on the number of CBVs}
    \label{fig:cbv-grid-search}
\end{figure}

>>>>

A runnable example of SAP flux correction for target \texttt{KOI 8462852}
can be written as follows
\begin{verbatim}
from pyke.lightcurve import KeplerCBVCorrector
cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
                         "0084/008462852/kplr008462852-2011073133259_llc.fits")
cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

As a result, Fig~\ref{fig:cbv-correction} illustrates the correction.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv.pdf}
    \caption{CBV correction applied on \texttt{KOI 8462852}}
    \label{fig:cbv-correction}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-grid-search.pdf}
    \caption{Grid search on the number of CBVs}
    \label{fig:cbv-grid-search}
\end{figure}
